Long-Term Reproducibility through Replication:\\ the ReScience Initiative

### 2017-06-08 draft.tex
Added all editors & active reviewers, miss publication authors

% Better default font (Libertine and Inconsolata)
% \usepackage[ttscale=.875]{libertine}
% \usepackage[scaled=0.96]{zi4}

\usepackage{mathspec}
\setmainfont{Minion Pro Cond}
\setmathsfont(Digits,Greek,Latin)[Numbers={Proportional}]{Minion Pro}
\setmathrm{Minion Pro}
\setsansfont{MyriadPro-Cond}

@@

% Headers
\usepackage{fancyhdr}
\pagestyle{fancy}
% \fancyhf{}
\rhead{\footnotesize \sf page \thepage}
\lhead{\footnotesize \sf Rougier et al. 2017
       \textbullet~The ReScience Initiative}
\rfoot{}
\cfoot{}
\lfoot{}

@@

@@

\title{Long-Term Reproducibility through Replication:\\
       the ReScience Initiative}
\author{%
  \textbf{Nicolas P. Rougier}$^{1,2,3,*}$,
  \textbf{Konrad Hinsen}$^{4,5}$,
  \textbf{Thomas Arildsen}$^{?}$,
  \textbf{Lorena Barba}$^{?}$,
  \textbf{Fabien Benureau}$^{?}$,
  \textbf{C. Titus Brown}$^{?}$,
  \textbf{Georgios Detorakis}$^{?}$,
  \textbf{Emmanuelle Gouillart}$^{?}$,
  \textbf{Pierre de Buyl}$^{?}$,
  \textbf{Benoît Girard}$^{?}$,
  \textbf{Olivia Guest}$^{?}$,
  \textbf{Mehdi Khamassi}$^{?}$,
  \textbf{Etienne Roesch}$^{?}$,
  \textbf{Joseph Stachelek}$^{?}$,
  \textbf{Owen Petchey}$^{?}$,
  \textbf{Timothée Poisot}$^{?}$,
  \textbf{Karthik Ram}$^{?}$,
  \textbf{Yoav Ram}$^{?}$
  \textbf{Federico Vaggi}$^{?}$,
  \textbf{Julien Vitay}$^{?}$,
  \textbf{Tiziano Zito}$^{?}$\\
  \begin{footnotesize}
    $^{1}$INRIA Bordeaux Sud-Ouest
          Talence, France
    $^{2}$Institut des Maladies Neurodégénératives, Université de Bordeaux,
          CNRS, UMR 5293, Bordeaux, France
    $^{3}$LaBRI, Université de Bordeaux, Institut Polytechnique de Bordeaux,
          CNRS, UMR 5800, Talence, France
    $^{4}$Centre de Biophysique Moléculaire,
          CNRS UPR4301, Orléans Cedex 2
    $^{5}$Synchrotron SOLEIL, Division Expériences,
          Gif sur Yvette, France\\
    $^{*}$Corresponding author:
          \href{mailto:Nicolas.Rougier@inria.fr}{Nicolas.Rougier@inria.fr}          
  \end{footnotesize}
}

>>>>

% Better default font (Libertine and Inconsolata)
\usepackage[ttscale=.875]{libertine}
\usepackage[scaled=0.96]{zi4}

%% \usepackage{mathspec}
%% \setmainfont{Minion Pro Cond}
%% \setmathsfont(Digits,Greek,Latin)[Numbers={Proportional}]{Minion Pro}
%% \setmathrm{Minion Pro}
%% \setsansfont{MyriadPro-Cond}

@@

% Headers
\usepackage{fancyhdr}
\pagestyle{fancy}
% \fancyhf{}
\rhead{\footnotesize \sf page \thepage}
\lhead{\footnotesize \sf Rougier, Hinsen et al. 2017
       \textbullet~The ReScience Initiative}
\rfoot{}
\cfoot{}
\lfoot{}

@@

\newcommand{\hgap}{\hspace{1mm}}

@@

\title{Long-Term Reproducibility through Replication:\\
       the ReScience Initiative}
\author{%
  \begin{small}
\textbf{Nicolas P. Rougier}$^{1,*}$\href{http://orcid.org/0000-0002-6972-589X}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Konrad Hinsen}$^{2}$\href{http://orcid.org/0000-0003-0330-9428}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Thomas Arildsen}$^{3}$\href{http://orcid.org/0000-0003-3254-3790}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Lorena Barba}$^{4}$\href{http://orcid.org/0000-0001-5812-2711}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Fabien C. Y. Benureau}$^{5}$\href{http://orcid.org/0000-0003-4083-4512}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{C. Titus Brown}$^{6}$\href{http://orcid.org/0000-0001-6001-2677}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Pierre de Buyl}$^{7}$\href{http://orcid.org/0000-0002-6640-6463}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Andrew Davison}$^{8}$\href{http://orcid.org/0000-0002-4793-7541}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Marc André Delsuc}$^{9}$\href{http://orcid.org/0000-0002-1400-5326}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Georgios Detorakis}$^{10}$\href{http://orcid.org/0000-0001-5891-1702}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Damien Drix}$^{11}$\href{http://orcid.org/0000-0003-4107-5693}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Pierre Enel}$^{12}$\href{http://orcid.org/0000-0001-8983-6223}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Benoît Girard}$^{13}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Emmanuelle Gouillart}$^{14}$\href{http://orcid.org/0000-0002-3869-9967}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Olivier Grisel}$^{15}$\href{http://orcid.org/0000-0002-8226-4012}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Olivia Guest}$^{16}$\href{http://orcid.org/0000-0002-1891-0972}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Matt Hall}$^{17}$\href{http://orcid.org/0000-0002-9530-5477}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Xavier Hinaut}$^{18}$\href{http://orcid.org/0000-0002-1924-1184}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Mehdi Khamassi}$^{19}$\href{http://orcid.org/0000-0002-2515-1046}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Almar Klein}$^{20}$\href{http://orcid.org/0000-0002-9978-2780}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Pietro Marchesi}$^{21}$\href{http://orcid.org/0000-0001-5955-6909}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Dan McGlinn}$^{22}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Hans Ekkehard Plesser}$^{23}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Timothée Poisot}$^{24}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Karthik Ram}$^{25}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Yoav Ram}$^{26}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Etienne Roesch}$^{27}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Cyrille Rossant}$^{28}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Aaron Shifman}$^{29}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Joseph Stachelek}$^{30}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Marcel Stimberg}$^{31}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Federico Vaggi}$^{32}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Julien Vitay}$^{33}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Anya Vostinar}$^{34}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Roman Yurchak}$^{35}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{iD-icon.pdf}},
\textbf{Tiziano Zito}$^{36}$,
\textbf{Ozan Çağlayan}$^{37}$\href{http://orcid.org/0000-0002-5992-3470}{\includegraphics[width=8pt]{iD-icon.pdf}}\\
\end{small}
\begin{footnotesize}
  \vspace{2mm}
    $^{1}$INRIA Bordeaux Sud-Ouest
          Talence, France --
          Institut des Maladies Neurodégénératives, Université de Bordeaux,
          CNRS UMR 5293, Bordeaux, France -- 
          LaBRI, Université de Bordeaux, Institut Polytechnique de Bordeaux,
          CNRS UMR 5800, Talence, France •
    $^{2}$Centre de Biophysique Moléculaire,
          CNRS UPR4301, Orléans --
          Synchrotron SOLEIL, Division Expériences,
          Gif sur Yvette, France\\
    $^{*}$Corresponding author:
          \href{mailto:Nicolas.Rougier@inria.fr}{Nicolas.Rougier@inria.fr}          
  \end{footnotesize}
}
